---
title: "Harvard|Choose Your Own Project| Swedish Data Crime"
author: "Edy Susanto"
output:
  word_document:
    toc: yes
    toc_depth: '2'
  pdf_document:
    toc: yes
    toc_depth: 2
  html_document:
    toc: yes
    toc_depth: '2'
    df_print: paged
---
```{r setup, warning = FALSE, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r , message=FALSE, warning=FALSE, echo=FALSE}

if(!require(tidyverse)) install.packages("tidyverse")
if(!require(kableExtra)) install.packages("kableExtra")
library(dplyr)
library(tidyverse)
library(kableExtra)
```
## Part 1 Introduction

Crime analysis and prevention is a systematic approach for identifying and analyzing patterns and trends in crime. Our system can predict regions which have high probability for crime occurrence and can visualize crime prone areas.

## Part 2 Project Goal

This project will mainly focus on creating a Classification Machine Learning System
using Swedish Data Crime.
This data set contains statistics on reported crimes in Sweden (by 100.000) from 1950 to 2015. It contains the following columns:

crimes.total: total number of reported crimes
crimes.penal.code: total number of reported crimes against the criminal code
crimes.person: total number of reported crimes against a person
murder: total number of reported murder
sexual.offences: total number of reported sexual offences
rape: total number of reported rapes
assault: total number of reported aggravated assaults
stealing.general: total number of reported crimes involving stealing or robbery
robbery: total number of reported armed robberies
burglary: total number of reported armed burglaries
vehicle.theft: total number of reported vehicle thefts
house.theft: total number of reported theft inside a house
shop.theft: total number of reported theft inside a shop
out.of.vehicle.theft: total number of reported theft from a vehicle
criminal.damage: total number of reported criminal damages
other.penal.crimes: number of other penal crime offenses
fraud: total number of reported frauds
narcotics: total number of reported narcotics abuses
drunk.driving: total number of reported drunk driving incidents
Year: the year
population: the total estimated population of Sweden at the time

Link for the datasets is https://www.kaggle.com/mguzmann/swedishcrime

## Part 3.Load Requirement Packages

Load all packages dan all libraries into RStudio

```{r Install packages and load libraries, message=FALSE, warning=FALSE, echo=FALSE}

# Install libraries if not exist

if(!require(caret)) install.packages("caret")
if(!require(data.table)) install.packages("data.table")
if(!require(tidyr)) install.packages("tidyr")
if(!require(stringr)) install.packages("stringr")
if(!require(forcats)) install.packages("forcats")
if(!require(ggplot2)) install.packages("ggplot2")
if(!require(funModeling)) install.packages("funModeling")

# Loading all needed libraries

library(dslabs)
library(caret)
library(tidyr)
library(stringr)
library(forcats)
library(ggplot2)
library(gam)
library(splines)
library(foreach)
library(mgcv)
library(nlme)
library(data.table)
library(funModeling)
```

## Part 2 Load Dataset

```{r Read reported.csv and Change col names, echo=FALSE, message=FALSE, warning=FALSE}

urlfile <-
  "https://raw.githubusercontent.com/siedysoes/swedishcrime/main/reported.csv"

Crimes <- read.csv(urlfile, header = TRUE) # this is our working dataset
data(Crimes)
head(Crimes)
```
## Part 4.Data exploration and visualization

The dataset is a data table made of 21 (columns) and a total of  observations (67 rows).  

```{r Show head of Swedish Crime Data, message=FALSE, warning=FALSE, echo=FALSE}

Crimes %>% as_tibble()

```

Number of NA into the dataset:

```{r Show NA, message=FALSE, warning=FALSE, echo=FALSE}

map_int(Crimes, function(.x) sum(is.na(.x)))
```

There No Missing Value on Data Set

Show Proportion Crimes Data On Plot

```{r Show proportion and distrib Crimes, message=FALSE, warning=FALSE, echo=FALSE}

plot(Crimes$crimes.person, Crimes$Year)
temp_dataset <- Crimes

scatter.smooth(Crimes)
```


We can see that there are total crimes in Swedish is increase by Year

## Part 5 Pre Data Processing

**Principal Component Analysis(PCA)**

We can get variable importance without using a predictive model using information theory, ordered from highest to lowest:  

```{r}

variable_importance = var_rank_info(Crimes, "Year")
variable_importance

ggplot(variable_importance, aes(x = reorder(var, gr), y = gr, fill = var)) + 
  geom_bar(stat = "identity") + 
  coord_flip() + 
  theme_bw() + 
  xlab("") + 
  ylab("Variable Importance (based on Information Gain)") + 
  guides(fill = FALSE)
```


As we can see in the graphic, the displacement variable is the most important for our predictive model. We can see that the most crimes happen in Swedish is House Theft



```{r}
set.seed(1)
pca <- prcomp(Crimes %>% select(Year), scale = TRUE, center = TRUE)

str(pca)

summary(pca)

set.seed(1) 
# set.seed(1, sample.kind="Rounding") if using R 3.5.3 or later

test_index <- createDataPartition(y = Crimes$Year,
                                  times = 1, p = 0.2, list = FALSE) 
edx <- Crimes[-test_index,]
validation <- Crimes[test_index,]

#We will split edx data into train_set and test_set.

set.seed(1)
test_index <- createDataPartition(y = edx$Year,
                                  times = 1, p = 0.2, 
                                  list = FALSE)  # test_set 20%
train_set <- edx[-test_index,]
test_set <- edx[test_index,]

```

## Part 6 Building Model

```{r}


###
models <- c("glm", "lda", "naive_bayes", "svmLinear",
            "gamLoess", "qda", "knn", "kknn",
            "gam", "rf", "ranger", "wsrf", "mlp")

control <- trainControl(method = "cv",   # cross validation
                        number = 10,     # 10 k-folds or number 
                                  # of resampling iterations
                        repeats = 5)

data_train <- train_set       # first value for data parameter
data_test <-  test_set        # first we´ll use train and test dataset 
true_value <- test_set$Year # true outcome from test_set 
```

## Part 7 Prediction 
```{r}

#####
model <- train(Year ~ crimes.total,
               data = Crimes,
               method = "lm")

model

fitControl <- trainControl(method = "repeatedcv",   
                           number = 10,     # number of folds
                           repeats = 5)    # repeated five times

model.cv <- train(Year ~ crimes.total,
               data = Crimes,
               method = "lm",  # now we're using the lm method
               trControl = fitControl)  

model.cv   

predictions <- predict(model.cv, Crimes)

predictions

results <- sort(predictions)
barchart(predictions)
barplot.default(predictions)
plot.default(predictions)


```
## Part 8 Conclusion 

Our Model Has succesfully made with RMSE  5.38960 , which is valid for prediction in SWedish Data Crime.


